The watershed transform in ITK - discussion and new developments

### 2006-04-27 article/Article.tex
acknowledgments
darcs-hash:20060425150623-2fc9d-527fc267aabb5a8efedd6ab3fea99d8237f05f89.gz
rename Threshold attribute to Level to be consistent with ITK notation
darcs-hash:20060427092832-2fc9d-0eb7d917074f6ef3a26863a9dd791e8538044a84.gz

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=3.2]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=3.2]{threshold00-rgb}}
\subfigure[Minima threshold = 10]{\includegraphics[scale=3.2]{threshold10-rgb}}
\subfigure[Minima threshold = 20]{\includegraphics[scale=3.2]{threshold20-rgb}}
\subfigure[Minima threshold = 30 and Minima threshold = 40]{\includegraphics[scale=3.2]{threshold30-rgb}}
\subfigure[Minima threshold = 50]{\includegraphics[scale=3.2]{threshold50-rgb}}
\subfigure[markers]{\includegraphics[scale=3.2]{threshold-markers-rgb}}
\subfigure[Watershed from markers]{\includegraphics[scale=3.2]{threshold-markersMf-rgb}}
\caption{Different results of morphological watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image. All the watersheds were performed with $MarkWatershed = true$ and $FullyConnected = false$.}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=3.2]{threshold}}
\subfigure[No minima threshold]{\includegraphics[scale=3.2]{threshold00-itk-rgb}}
\subfigure[Level = 0.1]{\includegraphics[scale=3.2]{threshold10-itk-rgb}}
% \subfigure[Level = 0.2]{\includegraphics[scale=3.2]{threshold20-itk-rgb}}
\subfigure[Level = 0.4]{\includegraphics[scale=3.2]{threshold40-itk-rgb}}
\subfigure[Level = 0.63]{\includegraphics[scale=3.2]{threshold63-itk-rgb}}
\subfigure[Level = 0.65]{\includegraphics[scale=3.2]{threshold65-itk-rgb}}
\subfigure[markers]{\includegraphics[scale=3.2]{threshold-markers-rgb}}
\subfigure[Watershed from markers]{\includegraphics[scale=3.2]{threshold-markers-itk-rgb}}
\caption{Different results of ITK's watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image.}
\end{center}
\end{figure}

@@

\verb$MorphologicalWatershedImageFilter$ perform a watershed transformation
without marker. It encapsulate several filters:
\begin{itemize}
  \item \verb$HMinimaImageFilter$
  \item \verb$RegionalMinimaImageFilter$
  \item \verb$ConnectedComponentImageFilter$
  \item \verb$MorphologicalWatershedFromMarkersImageFilter$
\end{itemize}
While \verb$RegionalMinimaImageFilter$, \verb$ConnectedComponentImageFilter$,
and \verb$MorphologicalWatershedFromMarkersImageFilter$ are the usal steps
of the waterhed usage, the \verb$HMinimaImageFilter$ is a convenient way
to avoid the classical watershed's over segmentation by allowing the user
to select the dynamic of the minima. The minimum dynamic of minima can be
selected with \verb$SetThreshold()$.

@@

In this example, we use the watershed filter to split two nearly round
objects: the male and female pronucleus in a bovine embryo, around 18
hours after fecondation.

@@

The watershed is then performed to split the two pronucleus. A threshold
is used to avoid the too small minima in the border of the object and thus
avoid over segmentation. The label produced by the watershed are then
displayed on top of the original image.

@@

\small \begin{verbatim}
ws = itk.MorphologicalWatershedImageFilter.IUC2IUC2.New(idistance,
                                                        MarkWatershed=False,
                                                        Threshold=10)
mask = itk.MaskImageFilter.IUC2IUC2IUC2.New(ws, fill)
overlay = itk.LabelOverlayImageFilter.IUC2IUC2IRGBUC2.New(reader, mask, Opacity=0.5)
\end{verbatim} \normalsize

@@

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=3.2]{level}}
\subfigure[No minima level]{\includegraphics[scale=3.2]{level00-rgb}}
\subfigure[Minima level = 10]{\includegraphics[scale=3.2]{level10-rgb}}
\subfigure[Minima level = 20]{\includegraphics[scale=3.2]{level20-rgb}}
\subfigure[Minima level = 30 and Minima level = 40]{\includegraphics[scale=3.2]{level30-rgb}}
\subfigure[Minima level = 50]{\includegraphics[scale=3.2]{level50-rgb}}
\subfigure[markers]{\includegraphics[scale=3.2]{level-markers-rgb}}
\subfigure[Watershed from markers]{\includegraphics[scale=3.2]{level-markersMf-rgb}}
\caption{Different results of morphological watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image. All the watersheds were performed with $MarkWatershed = true$ and $FullyConnected = false$.}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image]{\includegraphics[scale=3.2]{level}}
\subfigure[No minima level]{\includegraphics[scale=3.2]{level00-itk-rgb}}
\subfigure[Level = 0.1]{\includegraphics[scale=3.2]{level10-itk-rgb}}
% \subfigure[Level = 0.2]{\includegraphics[scale=3.2]{level20-itk-rgb}}
\subfigure[Level = 0.4]{\includegraphics[scale=3.2]{level40-itk-rgb}}
\subfigure[Level = 0.63]{\includegraphics[scale=3.2]{level63-itk-rgb}}
\subfigure[Level = 0.65]{\includegraphics[scale=3.2]{level65-itk-rgb}}
\subfigure[markers]{\includegraphics[scale=3.2]{level-markers-rgb}}
\subfigure[Watershed from markers]{\includegraphics[scale=3.2]{level-markers-itk-rgb}}
\caption{Different results of ITK's watershed on an articial image. The labeled image are overlayed to the input image with {\em LabelOverlayImageFilter}. From $(b)$ to $(f)$, an example of reduction of the classical watershed over segmentation by minima dynamic filtering. $(g)$ and $(h)$ show a marker defined by a user, and the result over the input image.}
\end{center}
\end{figure}

@@

\verb$MorphologicalWatershedImageFilter$ perform a watershed transformation
without marker. It encapsulate several filters:
\begin{itemize}
  \item \verb$HMinimaImageFilter$
  \item \verb$RegionalMinimaImageFilter$
  \item \verb$ConnectedComponentImageFilter$
  \item \verb$MorphologicalWatershedFromMarkersImageFilter$
\end{itemize}
While \verb$RegionalMinimaImageFilter$, \verb$ConnectedComponentImageFilter$,
and \verb$MorphologicalWatershedFromMarkersImageFilter$ are the usal steps
of the waterhed usage, the \verb$HMinimaImageFilter$ is a convenient way
to avoid the classical watershed's over segmentation by allowing the user
to select the dynamic of the minima. The minimum dynamic of minima can be
selected with \verb$SetLevel()$.

@@

In this example, we use the watershed filter to split two nearly round
objects: the male and female pronucleus in a bovine embryo, around 22
hours after fecondation.

@@

The watershed is then performed to split the two pronucleus. A level
is used to avoid the too small minima in the border of the object and thus
avoid over segmentation. The label produced by the watershed are then
displayed on top of the original image.

@@

\small \begin{verbatim}
ws = itk.MorphologicalWatershedImageFilter.IUC2IUC2.New(idistance,
                                                        MarkWatershed=False,
                                                        Level=10)
mask = itk.MaskImageFilter.IUC2IUC2IUC2.New(ws, fill)
overlay = itk.LabelOverlayImageFilter.IUC2IUC2IRGBUC2.New(reader, mask, Opacity=0.5)
\end{verbatim} \normalsize

@@

\section{Acknowledgments}
We thank Dr Pierre Adenot and MIMA2 confocal facilities
(\url{http://mima2.jouy.inra.fr}) for providing ESCells image used for
timing and for the bovine embryo image.
